Semantics for the $ \lambda $-calculus

### 2024-03-26 report/chapters/univalent-foundations.tex
Write about universe levels

>>>>

So if we have types and elements, are types also elements of some type? This is a tricky question, because if we say that there exists a type $ \TYPE $ which contains all types (and therefore, itself), we introduce inconsistency in our type system (see \cite{girard}). This is just like having a `set of all sets', which results in problematic questions like ``does its subset, containing only the sets which do not contain itself, contain itself?'' This is usually solved by either stating that types do not themselves have a type, or by assuming the existence of \textit{type universes} $ U_1, U_2, \dots $, such that every type is an element of some $ U_i $. Note that universes are allowed to be inclusive or not: we may have $ U_n \subseteq U_{n + 1} $. In this thesis, we will not explicitly mention particular universes. We will just write $ \TYPE $ to denote some type universe (or its category of types and functions). This is called \textit{typical ambiguity}, meaning that every theorem holds for all (suitable) assignments of universes to these instances of $ \TYPE $.
